\documentclass[11pt,draft]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{tabularx}

\newcolumntype{S}{X}
\newcolumntype{D}{>{\hsize=2cm}X}

\newcommand{\printsigndate}[1]{%
    \vspace{5mm}
    \begin{tabularx}{\textwidth}{S S D}
        \hrulefill{} & \hrulefill{} & \hrulefill{} \\
        \strut{}#1\strut{}&
        \strut{}#1 Signature\strut{}&
        \strut{}Date\strut{}
    \end{tabularx}%
}

\def\TheRelease{Release}
\def\TheInstallers{Installers}
\def\AnInstaller{Installer}

\begin{document}

\begin{center} \LARGE
    Installfest Release Form
\end{center}

\vspace{1em}

This Release Agreement (``\TheRelease'') is an agreement between you and
the members of the \textbf{UMBC Linux Users Group} and \emph{all event
attendees} who work on your computer on the behalf of the UMBC Linux
Users Group (``\TheInstallers''). By signing this Release, you agree to
waive your right to pursue legal action and you should therefore read
this \TheRelease{} carefully. If you have any questions about the legal
effect of this agreement, you should consult an attorney. Please be
aware that you may not participate in the event unless you have read and
signed this \TheRelease. By signing this \TheRelease{}, you acknowledge
the following:

\begin{enumerate}
\item that your signing this agreement is partial consideration for the
    services provided by the \TheInstallers{}.

\item that \TheInstallers{} do not promise that the work done on your
    computer equipment will be successful; an \AnInstaller{} will help
    you attempt to install and/or configure the Linux operating system,
    but possible defects in computer software or computer hardware may
    lead to undesirable results.

\item that the attempt to install and/or configure the Linux operating
    system poses potential dangers that no amount of care, caution,
    instruction, or expertise can eliminate.

\item that the attempt to install and/or configure the Linux operating
    system may result in the loss of some or all of the data stored on
    your computer's hard disks.

\item that many computer components, peripherals, and systems will be
    present, and you are responsible for the security of your personal
    property.

\item that you are expressly assuming the risks of the dangers set forth
    above.

\item that by signing this release agreement, you hereby forever release
    the \TheInstallers{} from any legal liability that arises from the
    attempt to install and/or configure the Linux operating system; and
    that this release includes, but is not limited to, any losses caused
    by the negligence of any \AnInstaller{} who attempts to install
    and/or configure Linux on your computer equipment.

\end{enumerate}

\vfill

{\scshape I acknowledge that I have read this Release Agreement and that
    I understand the language and terminology contained within. I have
    been advised of the potential dangers involved in the process of
    installing and configuring my computer and other electronic
    equipment.
}

\begin{flushright}
\printsigndate{Attendee} \\
\printsigndate{Witness} \\
\end{flushright}

\end{document}
